Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes

### 2013-01-05 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}

@@

\teaser{\includegraphics[width=1\textwidth]{images/teaser_cup} \caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
from coarse model to enhancing the curvature obtained from Catmull-Clark
Subdivision and the use of constraints over coarse model with weight
vertex group in red.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modelling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for triangles and quads meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modelling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results in a real
production environment with software blender.
\end{abstract}

@@

@@

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for polygonal meshes composed
of triangles and quads. Also shows some results of curvature enhancement
applications in sculpting, subdivision and modelling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for meshes of arbitrary topology composed for triangles
and quads representing a larger spectrum of mesh that works with today
eliminating the need for preprocessing and allows the preservation
of the original topology. With this operator we proposed a method
to generate family of parameterized shapes, in a robust and predictable
way. Our method enable to customization of smoothness and curvature
obtained during subdivision surfaces process. We proposed a new brush
for enhance silhouette features of mesh in modeling and sculpting.

@@

We design a new brush that allows enhancement of the curvatures of
a polygon mesh in real time. Our brush work well with the stroke method
\textsl{Drag Dot} developed in the sculpt mode in Blender \cite{blender}
which allows you to preview the change that occurs in the model until
you release the mouse button or tablet, also enable moves the mouse
over the model to fit exactly where you want to perform the enhancement
of the curvature.

@@

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for triangles
and quads TQLBO with several example models in figures \ref{fig:Spectrum},\ref{fig:camello_enhanced}.
We test the curvature enhance with TQLBO method on a PC with AMD Quad-Core
Processor @ 2.40 GHz and 8 GB RAM.

@@

\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
(c) for triangles, (d) for quads, (e) for triangles and quads random
chosen.}

\end{figure}

Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
smoothing operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

@@

@@

We wold like to thank Eduardo Romero and CIM\&LAB Computer Imaging
\& Medical Applications Laboratory for their support of our research.

>>>>

% Author and Affiliation (multiple authors).
\author{paper 000X }
%\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
%\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
%\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
\pdfauthor{Anonymous}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for hybrid quad/triangle meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modeling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results.
\end{abstract}

@@

\TOGlinkslist

@@

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for hybrid quad/triangle
meshes. Also shows some results of curvature enhancement applications
in sculpting, subdivision and modeling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
spectrum of mesh that works with today eliminating the need for preprocessing
and allows the preservation of the original topology. With this operator
we proposed a method to generate family of parameterized shapes, in
a robust and predictable way. Our method enable to customization of
smoothness and curvature obtained during subdivision surfaces process.
We proposed a new brush for enhance silhouette features of mesh in
modeling and sculpting.

@@

We design a new brush that allows enhancement of the curvatures of
a polygon mesh in real time. Our brush work well with the stroke method
named \textsl{Drag Dot}  which allows you to preview the change that
occurs in the model until you release the mouse button or tablet,
also enable moves the mouse over the model to fit exactly where you
want to perform the enhancement of the curvature.

@@

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for hybrid quad/triangle
meshes with several example models in figures \ref{fig:Spectrum},
\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
GHz and 8 GB RAM.

Figure \ref{fig:TQLBO_test} show the results when applying Laplace
Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

@@

\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
(c) for triangles, (d) for quads, (e) for triangles and quads random
chosen.}
\end{figure}

@@

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
brush for sculpting in real time. One pass was used with the brush
as shown in the figure with the blue and red radius. In the bottom
of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process. In figure \ref{fig:Performance-sculpt}
we show the performance of curvature enhancement brush, in this experimet
we use three models with 12K, 40K and 164K vertices, this models were
sculpted with curvature enhance brush in eache step the brush sphere
contain a variable number of vertices for processing. The processing
time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
times are good, because usually an artist sculpts a model for parts,
and each part is represented by an average of about 3000 vertices
in the models we use.

@@

We wold like to thank  anonymous friends for their support of our
research.
